---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---



```{r preprocess,eco=TRUE}
   
    library(lubridate)
    library(dplyr)
    library(ggplot2)
    library(missForest)
    library(chron)

    download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",destfile="data.zip")
    unzip("data.zip")
    data<-read.csv("activity.csv")
    head(data)
```




## What is mean total number of steps taken per day?
```{r stepperday_1,echo=TRUE}
    #changing date from char  to date class then subsetting 
    data[,2]<-ymd(data[,2])
    plot1<- data %>% group_by(data[,2])%>% summarise(sum=sum(steps,na.rm=TRUE))
    plot1<-as.data.frame(plot1)
    hist(plot1$sum,
     main="TOTAL STEPS PER DAY",
     xlab="Date",
     col="red")
```
**SUMMARY OF DATA - MEAN AND MEDIAN**
```{r stepperday_2,echo=TRUE}
    #mean and median 
    summary(plot1$sum)
```




## What is the average daily activity pattern?
```{r timeseries,echo=TRUE}
    tseries<-data%>% group_by(interval)%>%summarise(avg=mean(steps,na.rm=TRUE))
    tseries<-as.data.frame(tseries)
    ggplot(tseries,aes(interval,avg))+geom_line(col="red")
```

```{r timeseries_2, echo=TRUE}
   tseries[which.max(tseries$avg),]
```




## Imputing missing values
```{r totalna , echo=TRUE}
   sum(is.na(data))
```
```{r imputed, echo=TRUE}
   imputed<-data%>% group_by(interval)%>%summarise(mi=mean(steps,na.rm=TRUE))
   imputed<-as.data.frame(imputed)
   imputed[,2]<-round(imputed[,2])
   bata<-data
   for(i in 1:nrow(bata))
   {
        if(is.na(bata[i,1]))
        bata[i,1]<-imputed[which(imputed[,1]==bata[i,3]),2]
    }
    head(bata)
```
**Ploting the histogram of the imputed data**

```{r plotimputed, echo=TRUE}
    bata[,2]<-ymd(bata[,2])
    pimpu<-bata%>%group_by(bata[,2])%>%summarise(sums=sum(steps))
    pimpu<-as.data.frame(pimpu)
    hist(pimpu[,2],breaks=5,col="red",xlab="intervals",main="IMPUTED DATA")
```
**Imputung the data deacrese biasness in the data**
```{r summaryimputed, echo=TRUE}
   summary(pimpu[,2])
```
**we see that mean and median both increases after imputing missing values**

## Are there differences in activity patterns between weekdays and weekends?


```{r week, echo=TRUE}
    chk<-weekdays(bata$date)
    chk<-as.data.frame(chk)
    names(chk)<-"week"
    chk[which(chk[,1]=="Saturday"|chk[,1]=="Sunday"),1]="weekend"
    chk[which(chk[,1]!="weekend"),1]="weekdays"
```

**Now we will draw the plot** 
```{r weekdraw, echo=TRUE}
    bata<-cbind(bata,chk)
    wplot<-bata%>% group_by(interval,week) %>% summarise(means=mean(steps,na.rm=TRUE))
    wplot$week <- factor(wplot$week)
    ggplot(wplot,aes(interval,means))+geom_line(col="red")+facet_grid(week~.)
```    

```{r }
```


